---
title: "Process data"
author: "Abhisindh"
date: "`r Sys.Date()`"
output: html_document
---

```{r include=FALSE}
# packages
library(readr)

```

# Daily Activity

```{r}
Activity <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/dailyActivity_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Activity <- distinct(Activity)
```

No duplicate data found *(There are 33 distinct Id as opposed to 30 as expected, there is not enough information to find which is duplicate, so we are assuming all 33 Id s as distinct)*

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Activity %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrevelant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

```{r}
Activity$ActivityDate=as.POSIXct(Activity$ActivityDate, format="%m/%d/%Y", tz=Sys.timezone())
Activity$date <- format(Activity$ActivityDate, format = "%m/%d/%y")
Activity$ActivityDate=as.Date(Activity$ActivityDate, format="%m/%d/%Y", tz=Sys.timezone())
Activity$date=as.Date(Activity$date, format="%m/%d/%Y")
```

# Daily Calories

```{r}
Calories <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/dailyCalories_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Calories <- distinct(Calories)
```

No duplicate data found

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Calories %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrevelant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**


