---
title: "Process data"
author: "Abhisindh"
date: "`r Sys.Date()`"
output: html_document
---

```{r include=FALSE}
# packages
library(readr)
library(dplyr)

```

# 1.Activity

```{r}
Activity <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/dailyActivity_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Activity <- distinct(Activity)
```

No duplicate data found *(There are 33 distinct Id as opposed to 30 as expected, there is not enough information to find which is duplicate, so we are assuming all 33 Id s as distinct)*

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Activity %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrevelant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

```{r}
Activity$ActivityDate=as.POSIXct(Activity$ActivityDate, format="%m/%d/%Y", tz=Sys.timezone())
Activity$date <- format(Activity$ActivityDate, format = "%m/%d/%y")
Activity$ActivityDate=as.Date(Activity$ActivityDate, format="%m/%d/%Y", tz=Sys.timezone())
Activity$date=as.Date(Activity$date, format="%m/%d/%Y")
```

# 2.Calories

```{r}
Calories <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/dailyCalories_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Calories <- distinct(Calories)
```

No duplicate data found

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Calories %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrevelant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 3.Intesities

```{r}
Intensities <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/dailyIntensities_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Intensities <- distinct(Intensities)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
  Intensities %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**
```{r}
Intensities$ActivityDay=as.Date(Intensities$ActivityDay, format="%m/%d/%Y", tz=Sys.timezone())
```


# 4.Steps

```{r}
Steps <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/dailySteps_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Steps <- distinct(Steps)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Steps %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 5.Heartrate

```{r}
Heartrate <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/heartrate_seconds_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Heartrate <- distinct(Heartrate)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Heartrate  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 6.HourlyCalories

```{r}
HourlyCalories <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/hourlyCalories_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
HourlyCalories <- distinct(HourlyCalories)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
HourlyCalories  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 7.HourlyIntensities

```{r}
HourlyIntesities <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/hourlyIntensities_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
HourlyIntesities <- distinct(HourlyIntesities)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
HourlyIntesities  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**


# 8.HourlySteps

```{r}
HourlySteps <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/hourlySteps_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
HourlySteps <- distinct(HourlySteps)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
HourlySteps  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 9.MinuteCaloriesNarrow

```{r}
MinuteCaloriesNarrow <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteCaloriesNarrow_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteCaloriesNarrow <- distinct(MinuteCaloriesNarrow)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteCaloriesNarrow  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 10.MinuteCaloriesWide

```{r}
MinuteCaloriesWide <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteCaloriesWide_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteCaloriesWide <- distinct(MinuteCaloriesWide)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteCaloriesWide  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**


# 11.MinuteIntensitiesNarrow

```{r}
MinuteIntensitiesNarrow <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteIntensitiesNarrow_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteIntensitiesNarrow <- distinct(MinuteIntensitiesNarrow)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteIntensitiesNarrow  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 12.MinuteIntensitiesWide

```{r}
MinuteIntensitiesWide <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteIntensitiesWide_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteIntensitiesWide <- distinct(MinuteIntensitiesWide)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteIntensitiesWide  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 13.MinuteMETsNarrow

```{r}
MinuteMETsNarrow <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteMETsNarrow_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteMETsNarrow <- distinct(MinuteMETsNarrow)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteMETsNarrow  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 14.MinuteSleep

```{r}
MinuteSleep <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteSleep_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteSleep <- distinct(MinuteSleep)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteSleep  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 15.MinuteStepsNarrow

```{r}
MinuteStepsNarrow <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteStepsNarrow_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteStepsNarrow <- distinct(MinuteStepsNarrow)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteStepsNarrow  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 16.MinuteStepsWide

```{r}
MinuteStepsWide <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/minuteStepsWide_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
MinuteStepsWide <- distinct(MinuteStepsWide)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
MinuteStepsWide  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**

# 17.Sleep

```{r}
Sleep <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/sleepDay_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
Sleep <- distinct(Sleep)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
Sleep  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**
```{r}
Sleep$SleepDay=as.POSIXct(Sleep$SleepDay, format="%m/%d/%Y %I:%M:%S %p", tz=Sys.timezone())
Sleep$date <- format(Sleep$SleepDay, format = "%m/%d/%y")
Sleep$date=as.Date(Sleep$date, "% m/% d/% y")
```

# 18.WeightLog

```{r}
WeightLog <- read_csv("../Resources/Datasets/Fitabase Data 4.12.16-5.12.16/weightLogInfo_merged.csv")
```

-   [x] **Eliminate duplicate data.**

```{r}
WeightLog <- distinct(WeightLog)
```

No duplicate data found 

-   [x] **Repair incorrect data.** No incorrect data found
-   [x] **Handle missing data.**

```{r}
WeightLog  %>%
  summarise_all(~ sum(is.na(.)))
```

No missing data found

-   [x] **Remove irrelevant data.** No irrelevant data
-   [x] **Filter outlying data** No outlying data
-   [x] **Validate and QA data**
-   [x] **Formatting**