---
title: "Data description"
author: "Abhisindh"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Pacakges
library(stats)
library(Hmisc)
library(tidyverse)
library(readr)
```

# dailyActivity_merged

```{r include=FALSE}
dailyActivity_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/dailyActivity_merged.csv")
```

```{r echo=FALSE}
describe(dailyActivity_merged) %>% html()
```

<hr style="border:2px solid blue">

# dailyCalories_merged

```{r include=FALSE}
dailyCalories_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/dailyCalories_merged.csv")
```

```{r echo=FALSE}
describe(dailyCalories_merged) %>% html()
```

<hr style="border:2px solid blue">

# dailyIntensities_merged

```{r include=FALSE}
dailyIntensities_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/dailyIntensities_merged.csv")
```

```{r echo=FALSE}
describe(dailyIntensities_merged) %>% html()
```

<hr style="border:2px solid blue">

# dailySteps_merged

```{r include=FALSE}
dailySteps_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/dailySteps_merged.csv")
```

```{r echo=FALSE}
describe(dailySteps_merged) %>% html()
```

<hr style="border:2px solid blue">

# heartrate_seconds_merged

```{r include=FALSE}
heartrate_seconds_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/heartrate_seconds_merged.csv")
```

```{r echo=FALSE}
describe(heartrate_seconds_merged) %>% html()
```

<hr style="border:2px solid blue">

# hourlyCalories_merged

```{r include=FALSE}
hourlyCalories_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/hourlyCalories_merged.csv")
```

```{r echo=FALSE}
describe(hourlyCalories_merged) %>% html()
```

<hr style="border:2px solid blue">

# hourlyIntensities_merged

```{r include=FALSE}
hourlyIntensities_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/hourlyIntensities_merged.csv")
```

```{r echo=FALSE}
describe(hourlyIntensities_merged) %>% html()
```

<hr style="border:2px solid blue">

# hourlySteps_merged

```{r include=FALSE}
hourlySteps_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/hourlySteps_merged.csv")
```

```{r echo=FALSE}
describe(hourlySteps_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteCaloriesNarrow_merged

```{r include=FALSE}
minuteCaloriesNarrow_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteCaloriesNarrow_merged.csv")
```

```{r echo=FALSE}
describe(minuteCaloriesNarrow_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteCaloriesWide_merged

```{r include=FALSE}
minuteCaloriesWide_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteCaloriesWide_merged.csv")
```

```{r echo=FALSE}
describe(minuteCaloriesWide_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteIntensitiesNarrow_merged

```{r include=FALSE}
minuteIntensitiesNarrow_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteIntensitiesNarrow_merged.csv")
```

```{r echo=FALSE}
describe(minuteIntensitiesNarrow_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteIntensitiesWide_merged

```{r include=FALSE}
minuteIntensitiesWide_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteIntensitiesWide_merged.csv")
```

```{r echo=FALSE}
describe(minuteIntensitiesWide_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteMETsNarrow_merged

```{r include=FALSE}
minuteMETsNarrow_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteMETsNarrow_merged.csv")
```

```{r echo=FALSE}
describe(minuteMETsNarrow_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteSleep_merged

```{r include=FALSE}
minuteSleep_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteSleep_merged.csv")
```

```{r echo=FALSE}
describe(minuteSleep_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteStepsNarrow_merged

```{r include=FALSE}
minuteStepsNarrow_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteStepsNarrow_merged.csv")
```

```{r echo=FALSE}
describe(minuteStepsNarrow_merged) %>% html()
```

<hr style="border:2px solid blue">

# minuteStepsWide_merged

```{r include=FALSE}
minuteStepsWide_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/minuteStepsWide_merged.csv")
```

```{r echo=FALSE}
describe(minuteStepsWide_merged) %>% html()
```

<hr style="border:2px solid blue">

# sleepDay_merged

```{r include=FALSE}
sleepDay_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/sleepDay_merged.csv")
```

```{r echo=FALSE}
describe(sleepDay_merged) %>% html()
```

<hr style="border:2px solid blue">

# weightLogInfo_merged

```{r include=FALSE}
weightLogInfo_merged <- read_csv("D:/programming/Bellabeat_product_analysis/Resources/Bellabeat_Dataset/Fitabase Data 4.12.16-5.12.16/weightLogInfo_merged.csv")
```

```{r echo=FALSE}
describe(weightLogInfo_merged) %>% html()
```

<hr style="border:2px solid blue">
